Water resource utilization regimes at a basin scale: transition framework and development traps

### 2020-08-22 tex/main/manuscript.tex
整理讨论第一段

\subsection*{Transition Framework}
% 普遍存在的稳态转换可以由渐变或突变造成，而人类压力在世界范围内都是稳态转换最重要的驱动因素之一。
Widespread regime shift of coupled systems can be caused by gradual or abrupt changes, 
where anthropogenic stresses are among the most important drivers of. 
% 而随着人类干预的加深，水循环出现了自然-社会二元结构，主导当前人水系统的互馈过程。
With the accumulation of human interventions, 
a natural-social binary structure of the water cycle has emerged, 
dominating the current feedbacks of the human-water systems.
% 我们的研究结果表明，与社会-生态系统的过渡过程类似，水资源利用体系的变化也存在类似稳态转换的阶段性特征，并最终呈现出自然-社会二元结构。
According to our results, 
regime shifts as transitional phases of water utilization regimes, 
similar to evolution of social-ecological system, 
is one of the most important characteristics towards natural-social binary structure.
% 因此，我们在总结黄河流域变化过程的基础上，进一步概念化了水资源利用制度的过渡框架。
As such, we summarized a transition framework of the water utilization regimes, which conceptualizes a general trajectory towards a natural-social binary water cycle.

\begin{figure*}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/framework}
	\caption{
		Transition framework of the water utilization regime towards natural-social binary cycle.
		\textbf{A. Natural cycle:} As a kind of direct provisioning resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
		\textbf{B. Local binary cycle:} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions.
		However, as their ecological services generated through the socio-economic cycle, water resources play a non-provisioning role. What's more, better organized socio-economic system and developed technology gives humans the will and ability to better manage water resources and change since this phase, with intensive intervention in the natural water cycle. 
		\textbf{C. Basin binary cycle:} Entering this phase, with further developing in more economically efficient industries and services, trade-off between whose water demands with provisional water demands becomes prominent. Rather than determined by local socio-economic systems, water withdrawals and management act as considerations within the entire basin more, therefore. 
	}
	\label{fig:framework}
\end{figure*}

>>>>

\subsection*{Transition Framework}
% 普遍存在的稳态转换可以由渐变或突变造成，而人类压力在世界范围内都是稳态转换最重要的驱动因素之一。
Widespread regime shifts in a human-water system can be triggered by accumulation of gradual changes, where increasing anthropogenic pressure are among the most important drivers \cite{rochaCascadingRegimeShifts2018a,falkenmarkUnderstandingWaterResilience2019}. 
% 而随着人类干预的加深，水循环出现了自然-社会二元结构，主导当前人水系统的互馈过程。
At the same time, human society has become more and more dependent on water utilization as it further develops, modifying natural water cycles by socio-economic processes \cite{gleesonIlluminatingWaterCycle2020,dibaldassarreSociohydrologyScientificChallenges2019}.
% 与社会-自然二元水循环理论
This social water cycle has linked to the natural water cycle through water withdraw, water utilization and drainage, forming a closed chain of interdependence, interconnection and mutual influence, which is consistent with nature-society dualistic water cycle theory 
\cite{qinTheoreticalFrameworkDualistic2014,liuDualisticWaterCycle2010}.
% 我们的研究结果表明，与社会-生态系统的过渡过程类似，水资源利用体系的变化也存在类似稳态转换的阶段性特征，并最终呈现出自然-社会二元结构。
According to our results, regime shifts as transitional phases of water utilization regimes, similar in social-ecological system, is one of the most important characteristics towards natural-social dualistic structure 
\cite{cummingImplicationsAgriculturalTransitions2014,cummingLinkingEconomicGrowth2018}.
% 因此，我们在总结黄河流域变化过程的基础上，进一步概念化了水资源利用制度的过渡框架。
As such, we summarized a transition framework of the water utilization regimes here, which conceptualizes a general trajectory towards a natural-social dualistic water cycle (Figure~\ref{fig:framework}).g

\begin{figure*}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/framework}
	\caption{
		Transition framework of the water utilization regime towards natural-social binary cycle.
		\textbf{A. Natural cycle:} As a kind of direct provisioning resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
		\textbf{B. Regional cycle:} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions.
		However, as their ecological services generated through the socio-economic cycle, water resources play a non-provisioning role. What's more, better organized socio-economic system and developed technology gives humans the will and ability to better manage water resources and change since this phase, with intensive intervention in the natural water cycle. 
		\textbf{C. Basinal cycle:} Entering this phase, with further developing in more economically efficient industries and services, trade-off between whose water demands with provisional water demands becomes prominent. Rather than determined by local socio-economic systems, water withdrawals and management act as considerations within the entire basin more, therefore. 
	}
	\label{fig:framework}
\end{figure*}
